Parallel Multi-objective Optimization Method for Finding Complete Set of Weakly Efficient Solutions

### 2017-10-18 2017/URAL-PDC/slides/slides.tex
u-pdc: update slides

\begin{frame}
  \frametitle{Optimization method}
Optimization method generates searh sequence \(\{x_k\}\) and consists of the following steps:
\begin{enumerate}
  \setlength{\itemindent}{.1in}
  \item[Step 1.] Sort the searh information (one-dimentional points) in increasing order.
  \item[Step 2.] Compute an approximation of the function \(\varphi(x)\).
  \item[Step 3.] For each interval \((x_{i-1}, x_i)\) compute quantity \(R(i)\), called characteristic.
  \item[Step 4.] Choose an interval \((x_{t-1}, x_t)\) with the greatest characteristic and
  compute objective \(f(y(x))\) in the point choosen using the descision rule \(d\):
  \begin{displaymath}
    x^{k+1}=d(t)\in (x_{t-1}, x_t)
  \end{displaymath}
  \item[Step 4.] If \(x_{t}-x_{t-1}<\varepsilon\) stop the method.
\end{enumerate}
\end{frame}

@@

\begin{frame}
  \frametitle{Results}
  Examples of numerical solutions:
  \begin{figure}[ht]
      \centering
      \subfloat{{\includegraphics[width=.5\textwidth]{../img/viennet.png}}}
      \subfloat{{\includegraphics[width=.5\textwidth]{../img/poloni.pdf} }}
  \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{Results (speedup in iterations)}
  \begin{table}
    \centering
    \begin{tabular}{|l|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|}
  \hline
  \textbf{Problem} & \multicolumn{4}{c|}{\(p\)}\\
  \cline{2-5}
    & \(2\) & \(4\) & \(8\) & \(16\)\\
  \hline
  Markin-Strongin & 2.02 & 4.07 & 7.95 & 15.31 \\
  \hline
  Fonseca and Fleming 2d & 1.86 & 3.06 & 6.71 & 11.14 \\
  \hline
  Fonseca and Fleming 3d & 1.51 & 4.51 & 8.82 & 15.23 \\
  \hline
  Viennet problem & 2.27 & 3.99 & 7.76 & 17.12\\
  \hline
  Poloni's problem & 1.96 & 3.91 & 7.87 & 16.67 \\
  \hline
  \end{tabular}
  \end{table}

\begin{frame}
  \frametitle{Results (speedup in time)}
  \begin{table}[ht]
    \centering
    \begin{tabular}{|l|p{1.6cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|}
  \hline
  \textbf{Problem} & \multicolumn{5}{c|}{\(p\)}\\
  \cline{2-6}
  &\(1\)(time, s) & \(2\) & \(4\) & \(8\) & \(16\)\\
  \hline
  Markin-Strongin & 104.47 & 1.97 & 3.65 & 6.79 & 9.90 \\
  \hline
  Fonseca and Fleming 2d & 118.95 & 1.85 & 2.81 & 5.79 & 6.40 \\
  \hline
  Fonseca and Fleming 3d & 554.45 & 1.51 & 4.14 & 8.05 & 10.69 \\
  \hline
  Viennet problem & 1488.6 & 2.22 & 3.64 & 6.98 & 13.49\\
  \hline
  Poloni's problem & 336.74 & 1.82 & 3.64 & 6.98 & 10.60 \\
  \hline
  \end{tabular}
  \end{table}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Optimization method}
Optimization method generates searh sequence \(\{x_k\}\) and consists of the following steps:
\begin{enumerate}
  \setlength{\itemindent}{.1in}
  \item[Step 1.] Sort the searh information (one-dimentional points) in increasing order.
  \item[Step 2.] Compute an approximation of the function \(\varphi(x)\).
  \item[Step 3.] For each interval \((x_{i-1}, x_i)\) compute quantity \(R(i)\), called characteristic.
  \item[Step 4.] Choose an interval \((x_{t-1}, x_t)\) with the greatest characteristic and
  compute objective \(f(y(x))\) in the point choosen using the descision rule \(d\):
  \begin{displaymath}
    x^{k+1}=d(t)\in (x_{t-1}, x_t)
  \end{displaymath}
  \item[Step 4.] If \(x_{t}-x_{t-1}<\varepsilon\) stop the method.
\end{enumerate}
\textit{\footnotesize	{Detailed description: Strongin R.G., Sergeyev Ya.D.: Global optimization with non-convex constraints. Sequential and parallel algorithms (2000), Chapter 7}}
\end{frame}

@@

\begin{frame}
  \frametitle{Results}
  The method was implemented on C++ language using OpenMP framework. All the experimants were carried out on
  2xIntel Sandy Bridge E5-2660 2.2 GHz (total 16 cores) with 64Gb RAM.

  Examples of numerical solutions:
  \begin{figure}[ht]
      \centering
      \subfloat{{\includegraphics[width=.5\textwidth]{../img/viennet.png}}}
      \subfloat{{\includegraphics[width=.5\textwidth]{../img/poloni.pdf} }}
  \end{figure}
\end{frame}

@@

%\begin{frame}
%  \frametitle{Results (speedup in iterations)}
%  \begin{table}
%    \centering
%    \begin{tabular}{|l|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|}
%  \hline
%  \textbf{Problem} & \multicolumn{4}{c|}{\(p\)}\\
%  \cline{2-5}
%    & \(2\) & \(4\) & \(8\) & \(16\)\\
%  \hline
%  Markin-Strongin & 2.02 & 4.07 & 7.95 & 15.31 \\
%  \hline
%  Fonseca and Fleming 2d & 1.86 & 3.06 & 6.71 & 11.14 \\
%  \hline
%  Fonseca and Fleming 3d & 1.51 & 4.51 & 8.82 & 15.23 \\
%  \hline
%  Viennet problem & 2.27 & 3.99 & 7.76 & 17.12\\
%  \hline
%  Poloni's problem & 1.96 & 3.91 & 7.87 & 16.67 \\
%  \hline
%  \end{tabular}
%  \end{table}
%
%\end{frame}
%
\begin{frame}
  \frametitle{Results (speedup in time)}

  \begin{table}[ht]
    \centering
    \begin{tabular}{|l|p{1.6cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|}
  \hline
  \textbf{Problem} & \multicolumn{5}{c|}{\(p\)}\\
  \cline{2-6}
  &\(1\)(time, s) & \(2\) & \(4\) & \(8\) & \(16\)\\
  \hline
  Markin-Strongin & 104.47 & 1.97 & 3.65 & 6.79 & 9.90 \\
  \hline
  Fonseca and Fleming 2d & 118.95 & 1.85 & 2.81 & 5.79 & 6.40 \\
  \hline
  Fonseca and Fleming 3d & 554.45 & 1.51 & 4.14 & 8.05 & 10.69 \\
  \hline
  Viennet problem & 1488.6 & 2.22 & 3.64 & 6.98 & 13.49\\
  \hline
  Poloni's problem & 336.74 & 1.82 & 3.64 & 6.98 & 10.60 \\
  \hline
  \end{tabular}
  \end{table}
\end{frame}

\begin{frame}
  \frametitle{Results (speedup and efficiency)}
  \begin{figure}[ht]
      \centering
      \subfloat{{\includegraphics[width=.5\textwidth]{./img/speedup.pdf}}}
      \subfloat{{\includegraphics[width=.5\textwidth]{./img/efficiency.pdf} }}
  \end{figure}
\end{frame}
